---
title: "Compute how much time your script takes"
author: "Paulo Icaro"
date: "2024-09-23"
hidedate: true
output: 
  github_document: 
---





<divs>

<!------------>
<!-- Part 1 -->
<!------------>

## Brief guidethrough

<p>
|       This routine helps you to track the time of your script. Put into few words, this library contains a function that is designed for accounting the elapsed time of a script or just a specific snippet in the code.
</p>


## The timer function
|       The **timer** function contains 3 arguments: script, type and name. 
*   ***script***: represents the routine to be run. The way the routine is inserted in the script depends on the next argument
*   ***type***: indicates whether it is a full script, just a snippet of a complete routine or its a mere code.
*   ***type***: 
    -   if ***type = 'full'*** you must specify the path of the script to be run on the previous argument.
    -   if ***type = 'snippet'*** you must apply, on the previous argument, the function on a piece of the code. 
    -   if ***type = 'simple'*** you must write the script inside the previous argument.
*   ***name*** (optional): use it if you want to give the routine a name.

|       Now we are going to see some examples. In the first scenario, we have a simple counter code (no script or snippet) which will print numbers from 1 to 10 considering a two seconds interval between each printing.


```{r Timer - Case 1, echo = TRUE, message = FALSE}

# ------------------------------------- #
# --- Example - Case 1: Simple Code --- #
# ------------------------------------- #

# --- Sourcing the library --- #
source('https://raw.githubusercontent.com/paulo-icaro/Script_Timer/main/Timer.R')


# --- Script to be used // Counter script - No need to execute it ! --- #
# for(i in 1:10){
#   print(i)
#   Sys.sleep(2)
# }


# --- Accounting the time elapsed --- #
timer(script = for(i in 1:10){print(i)
                              Sys.sleep(2)},
      type = 'simple',
      name = 'counter')
```


|       In the second case we will account the elapsed time of a complete script. You can either use a routine from a local machine -- with the path properly specified -- or from a github repository. In this case, we will call a library from this author repository on github. Probably it will take only one second for that. However the code is proved to be up and running.


```{r Timer - Case 2, echo = TRUE, message = FALSE}

# ------------------------------------- #
# --- Example - Case 2: Full Script --- #
# ------------------------------------- #

# --- Sourcing the library --- #
source('https://raw.githubusercontent.com/paulo-icaro/Script_Timer/main/Timer.R')


# --- Accounting the time elapsed --- #
timer(script = 'https://raw.githubusercontent.com/paulo-icaro/Bacen_API/main/Bacen_API.R',
      type = 'full',
      name = 'author_libary')
```


|       For the final situation we will apply the timer function on a part (snippet) of a script. In this example we will write this script instead of sourcing it. Have in mind that this doesn't mean that sourcing isn't possible.


``` {r Timer - Case 3 - Print Part, echo = TRUE, message = FALSE, results = 'hide'}

# --------------------------------- #
# --- Example - Case 3: Snippet --- #
# --------------------------------- #

# --- Sourcing the library --- #
source('https://raw.githubusercontent.com/paulo-icaro/Script_Timer/main/Timer.R')


# --- Script to be used // Counter script modified - No need to execute it ! --- #
# for(i in 1:10){
#   print(i)
#   Sys.sleep(2)
# }
# print(paste0('The result of the sum is', x))



# --- Script to be used // Counter script modified --- #
timer(script = for(i in 1:10){x = i + 1
                              Sys.sleep(2)},       # Accounting the time elapsed
      type = 'snippet',
      name = 'counter')    

print(paste0('The result of the sum is ', x))
```


``` {r Timer - Case 3 - Result Part, echo = FALSE, message = FALSE}

# --------------------------------- #
# --- Example - Case 3: Snippet --- #
# --------------------------------- #

# --- Sourcing the library --- #
source('https://raw.githubusercontent.com/paulo-icaro/Script_Timer/main/Timer.R')


# --- Script to be used // Counter script modified - No need to execute it ! --- #
# for(i in 1:10){
#   print(i)
#   Sys.sleep(2)
# }
# print(paste0('The result of the sum is', x))



# --- Script to be used // Counter script modified --- #
timer(script = for(i in 1:10){x = i + 1
                              Sys.sleep(2)},       # Accounting the time elapsed
      type = 'snippet',
      name = 'counter')    

print(paste0('The result of the sum is ', x))
```

\doublelinespace

#### Attention !
|   Make sure to use the correctly the script and time arguments. In fact the 'snippet' and 'simple' types work the same way. However, if you insert a full script and inform the type other option than 'full' the result will be shown incorrectly.

</divs>